---
title: "Credit Card Default Case Study"
author: "Dheeraj Kumar"
date: "2/13/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

## R Markdown

# Credit card Default Case Study

## Importing libraries 

```{r}

#install.packages("ggplot2")
#install.packages("dplyr")
#install.packages("psych")
#install.packages("MASS")
#install.packages("tidyverse")
#install.packages("corrplot")
#install.packages("leaps")
#install.packages("rpart")
#install.packages("mgcv")
#install.packages("glmnet")
#install.packages("boot")
#install.packages("caret")
#install.packages("rpart.plot")
#install.packages("tree")
#install.packages("plotmo")
#install.packages("ROCR")
#install.packages("PRROC")
#install.packages("pROC")

```

```{r}
library(ggplot2)
library(dplyr)
library(psych)
library(MASS)
library(tidyverse)
library(corrplot)
library(leaps)
library(rpart)
library(mgcv)
library(glmnet)
library(boot)
library(caret)
library(rpart.plot)
library(tree)
library(plotmo)
library(ROCR)
library(PRROC)
library(pROC)

```

## Importing the dataset

```{r}
credit_card_data <- read.csv("D:/UC/Classes/Spring/Data Mining 1/Credit Card Data/default_of_credit_card_clients.csv")
```

## Checking head

```{r}
head(credit_card_data)
```

## Renaming target variable

```{r}
credit_card_data <- rename(credit_card_data, default_payment_next_month = default.payment.next.month)
```

## Checking structure of dataset

```{r}
str(credit_card_data)
```

## Checking dimensions of dataset

```{r}
dim(credit_card_data)
```

## Checking for any missing values

```{r}
sum(is.na(credit_card_data)) 
```

## Checking statistics on variables

```{r}
summary(credit_card_data)
```

## Converting required variables to factors

```{r}
credit_card_data$SEX <- as.factor(credit_card_data$SEX)
credit_card_data$MARRIAGE <- as.factor(credit_card_data$MARRIAGE)
credit_card_data$EDUCATION <- as.factor(credit_card_data$EDUCATION)
credit_card_data$default_payment_next_month <- as.factor(credit_card_data$default_payment_next_month)
credit_card_data$PAY_0 <- as.factor(credit_card_data$PAY_0)
credit_card_data$PAY_2 <- as.factor(credit_card_data$PAY_2)
credit_card_data$PAY_3 <- as.factor(credit_card_data$PAY_3)
credit_card_data$PAY_4 <- as.factor(credit_card_data$PAY_4)
credit_card_data$PAY_5 <- as.factor(credit_card_data$PAY_5)
credit_card_data$PAY_6 <- as.factor(credit_card_data$PAY_6)
```

# Dropping ID column from dataset

```{r}
credit_card_data = subset(credit_card_data, select = -c(ID))
```

## Setting unique seed

```{r}
set.seed(14283873)
```

## Splitting dataset into Train and Test

```{r}
index <- sample(nrow(credit_card_data), nrow(credit_card_data) * 0.80)
```

## Creating Train and Test datasets

```{r}
credit_card_data_train <- credit_card_data[index, ]
credit_card_data_test <- credit_card_data[-index, ]
```

## Checking dimensions of Train and Test dataset

```{r}
dim(credit_card_data_train)  ## 24000,24

dim(credit_card_data_test)   ## 6000,24

```

#------------ A-1. Analysis with 80% Training Data ---------------------#

## Performing EDA

### Countplot of default_payment_next_month

```{r}
ggplot(credit_card_data_train,aes(default_payment_next_month))+geom_bar()+ggtitle("credit card default distribution")
```

## Distribution of default_payment_next_month vs SEX

```{r}
ggplot(credit_card_data_train,aes(SEX))+geom_bar(aes(fill=default_payment_next_month))+ggtitle("Credit Default distribution among SEX")
```

## Distribution of default_payment_next_month vs MARRIAGE

```{r}
ggplot(credit_card_data_train,aes(MARRIAGE))+geom_bar(aes(fill=default_payment_next_month))+ggtitle("Credit Default distribution among MARRIAGE")
```

## Distribution of default_payment_next_month vs EDUCATION

```{r}
ggplot(credit_card_data_train,aes(EDUCATION))+geom_bar(aes(fill=default_payment_next_month))+ggtitle("credit card distribution among EDUCATION")
```

## Distribution of default_payment_next_month vs PAY_0

```{r}
ggplot(credit_card_data_train,aes(PAY_0))+geom_bar(aes(fill=default_payment_next_month))+ggtitle("credit card distribution among PAY_0")
```

## Distribution of default_payment_next_month vs AGE

```{r}
ggplot(credit_card_data_train,aes(AGE))+geom_bar(aes(fill=default_payment_next_month))+ggtitle("credit card distribution among AGE")
```


#------------ A-2. Logistic Regression and Variable Selection ---------------------#

##----------------- Part 1 -----------------##

##----------------- Full Model -----------------##

## Logistic Regression with full model

```{r}
full.glm <- glm(default_payment_next_month ~ ., family=binomial, data = credit_card_data_train)
full.glm.summary <- summary(full.glm)
full.glm.summary
```

## Displaying coefficients of the full model

```{r}
data.frame(coef = round(full.glm$coefficients,2))
AIC(full.glm) # 20997.55
BIC(full.glm) # 21668.67
```

## Calculating in-sample residual deviance

```{r}
full.glm$deviance  # 20831.55
```

# Calculating Model mean residual deviance (in-sample)

```{r}
full.glm$dev/full.glm$df.residual # 0.8709933
```

# Plotting histogram for full model

```{r}
hist(predict(full.glm))
```

##----------------- Null Model -----------------##

## Logistic Regression with Null model

```{r}
null.glm=glm(default_payment_next_month ~ 1, family=binomial, data=credit_card_data_train)
null.glm.summary <- summary(null.glm)
null.glm.summary
```

## Displaying coefficients of the null model

```{r}
data.frame(coef = round(null.glm$coefficients,2))
AIC(null.glm) # 25497.03
BIC(null.glm) # 25505.12
```

## Calculating in-sample residual deviance

```{r}
null.glm$deviance  # 25495.03
```

# Calculating Model mean residual deviance (in-sample)

```{r}
null.glm$dev/null.glm$df.residual # 1.062337
```

# Plotting histogram for full model

```{r}
hist(predict(null.glm))
```

##----------------- Two Variable Model with EDUCATION and PAY_0 -----------------##

```{r}
two_var.glm <- glm(default_payment_next_month ~ credit_card_data_train$EDUCATION + credit_card_data_train$PAY_0, family=binomial, data=credit_card_data_train)
two_var.glm.summary <- summary(two_var.glm)
two_var.glm.summary
```

## Displaying coefficients of the two variable model

```{r}
data.frame(coef = round(two_var.glm$coefficients,2))
AIC(two_var.glm) # 21741.37
BIC(two_var.glm) # 21878.82
```

## Calculating in-sample residual deviance

```{r}
two_var.glm$deviance  # 21707.37
```

# Calculating Model mean residual deviance (in-sample)

```{r}
two_var.glm$dev/two_var.glm$df.residual # 0.9051147
```

##----------------- Part 2 -----------------##

## Performing stepwise variable selection with AIC and BIC

```{r}
credit_default_glm_back <- step(full.glm) 
summary(credit_default_glm_back)

credit_default_glm_back$deviance # 20833.88

AIC(credit_default_glm_back) # 20991.88

BIC(credit_default_glm_back) # 21630.66
```

# Calculating Model mean residual deviance (in-sample)

```{r}
credit_default_glm_back$dev/credit_default_glm_back$df.residual # 0.8709453
```

#------------ Stepwise variable selection using AIC ------------#
```{r}
model_stepwise_AIC <- step(null.glm, scope = list(lower= null.glm, upper= full.glm), direction = "both", k = 2)

# Lowest AIC = 20991.88
#default_payment_next_month ~ PAY_0 + PAY_3 + LIMIT_BAL + PAY_5 + 
#  PAY_AMT1 + MARRIAGE + EDUCATION + BILL_AMT2 + PAY_6 + PAY_4 + 
#  PAY_AMT2 + SEX + PAY_2 + PAY_AMT5 + PAY_AMT3 + PAY_AMT6 + 
#  AGE + BILL_AMT1 + BILL_AMT3

```

## Running model with selected variables

```{r}
model_stepwise_AIC.glm <- glm(default_payment_next_month ~ PAY_0 + PAY_3 + LIMIT_BAL + PAY_5 + 
                                PAY_AMT1 + MARRIAGE + EDUCATION + BILL_AMT2 + PAY_6 + PAY_4 + 
                                PAY_AMT2 + SEX + PAY_2 + PAY_AMT5 + PAY_AMT3 + PAY_AMT6 + 
                                AGE + BILL_AMT1 + BILL_AMT3, family=binomial, data=credit_card_data_train)

model_stepwise_AIC.glm_summary<-summary(model_stepwise_AIC.glm)

model_stepwise_AIC.glm_summary

AIC(model_stepwise_AIC.glm) # 20991.88

BIC(model_stepwise_AIC.glm) # 21630.66

model_stepwise_AIC.glm$deviance # 20833.88
```

# Calculating Model mean residual deviance (in-sample)

```{r}
model_stepwise_AIC.glm$dev/model_stepwise_AIC.glm$df.residual # 0.8709453
```


#------------ Stepwise variable selection using BIC ------------#

```{r}
model_stepwise_BIC <- step(null.glm, scope = list(lower= null.glm, upper= full.glm), direction = "both", k = log(nrow(credit_card_data_train)))

#Lowest AIC = 21385.83
#default_payment_next_month ~ PAY_0 + LIMIT_BAL + PAY_5 + PAY_AMT2 + 
#  PAY_AMT1 + BILL_AMT3 + MARRIAGE + SEX + PAY_AMT3

```

```{r}
model_stepwise_BIC.glm <- glm(default_payment_next_month ~ PAY_0 + LIMIT_BAL + PAY_5 + PAY_AMT2 + 
                               PAY_AMT1 + BILL_AMT3 + MARRIAGE + SEX + PAY_AMT3, family=binomial, data=credit_card_data_train)

model_stepwise_BIC.glm_summary<-summary(model_stepwise_BIC.glm)

model_stepwise_BIC.glm_summary

AIC(model_stepwise_BIC.glm) # 21151.34

BIC(model_stepwise_BIC.glm) # 21385.83

model_stepwise_BIC.glm$deviance # 21093.34
```

# Calculating Model mean residual deviance (in-sample)

```{r}
model_stepwise_BIC.glm$dev/model_stepwise_BIC.glm$df.residual # 0.8799525
```


##----------------- Part 3 -----------------##

## Performing LASSO variable selection

## Creating dummy variable for object datatypes

```{r}
dummy <- model.matrix(~ ., data = credit_card_data)
```

# Checking head of dummy matrix

```{r}

head(dummy)

credit_data_lasso <- data.frame(dummy[,-1])

set.seed(14283873)

index <- sample(nrow(credit_card_data),nrow(credit_card_data)*0.80)

credit_card_data_train_Y = credit_data_lasso[index,"default_payment_next_month1"]

credit_card_data_test_Y = credit_data_lasso[-index,"default_payment_next_month1"]

credit_card_data_train_X = as.matrix(dplyr::select(credit_data_lasso, -default_payment_next_month1)[index,])

credit_card_data_test_X = as.matrix(dplyr::select(credit_data_lasso, -default_payment_next_month1)[-index,])

```

## Checking dimensions

```{r}
str(credit_card_data_train_X)
str(credit_card_data_train_Y)
str(credit_card_data_test_X)
str(credit_card_data_test_Y)
```

#LASSO

```{r}
library(glmnet)
```

```{r}
credit_default_lasso <- glmnet(x=credit_card_data_train_X, y=credit_card_data_train_Y, family = "binomial")
```

## Performing cross-validation to determine the shrinkage parameter

```{r}
credit_lasso_cv <- cv.glmnet(x=credit_card_data_train_X, y=credit_card_data_train_Y, family = "binomial", type.measure = "class")
plot(credit_lasso_cv)
```

## Calculating coefficients using Lambda min

```{r}
coef(credit_default_lasso, s=credit_lasso_cv$lambda.min)

lasso.min.glm <- glm(default_payment_next_month ~ LIMIT_BAL + SEX + EDUCATION +
                       MARRIAGE +  AGE + PAY_0 + PAY_2 + PAY_3 + PAY_4 + PAY_5 +PAY_6 +
                       BILL_AMT1 + BILL_AMT2 + BILL_AMT3 + BILL_AMT4 + BILL_AMT5 + BILL_AMT6 +
                       PAY_AMT1 + PAY_AMT2 + PAY_AMT3 + PAY_AMT4 + PAY_AMT5 + PAY_AMT6, family = "binomial", data=credit_card_data_train)
```

```{r}
lasso.min.glm_summary<-summary(lasso.min.glm)

lasso.min.glm_summary
```

```{r}
AIC(lasso.min.glm) # 20997.55

BIC(lasso.min.glm) # 21668.67

lasso.min.glm$deviance # 20831.55
```

# Calculating Model mean residual deviance (in-sample)

```{r}
lasso.min.glm$dev/lasso.min.glm$df.residual # 0.8709933
```

## Calculating coefficients using Lambda 1se
```{r}
coef(credit_default_lasso, s=credit_lasso_cv$lambda.1se)

lasso.1se.glm <- glm(default_payment_next_month ~ LIMIT_BAL + SEX + EDUCATION +
                       MARRIAGE +  AGE + PAY_0 + PAY_2 + PAY_3 + PAY_4 + PAY_5 +PAY_6 +
                       PAY_AMT1 + PAY_AMT2 + PAY_AMT3 + PAY_AMT5 + PAY_AMT6, family = "binomial", data=credit_card_data_train)
```

```{r}
lasso.1se.glm_summary<-summary(lasso.1se.glm)

lasso.1se.glm_summary
```

```{r}
AIC(lasso.1se.glm) # 21023.12

BIC(lasso.1se.glm) # 21637.65

lasso.1se.glm$deviance # 20871.12

# Calculating Model mean residual deviance (in-sample)

lasso.1se.glm$dev/lasso.1se.glm$df.residual # 0.8723928
```

## Plotting graph for LASSO

#install.packages('glmnet')
```{r}
#library(glmnet)
```

```{r}
str(credit_card_data_train)

## Converting to integer for plotting 

credit_card_data_train$SEX <- as.integer(credit_card_data_train$SEX)
credit_card_data_train$MARRIAGE <- as.integer(credit_card_data_train$MARRIAGE)
credit_card_data_train$EDUCATION <- as.integer(credit_card_data_train$EDUCATION)
credit_card_data_train$default_payment_next_month <- as.integer(credit_card_data_train$default_payment_next_month)
credit_card_data_train$PAY_0 <- as.integer(credit_card_data_train$PAY_0)
credit_card_data_train$PAY_2 <- as.integer(credit_card_data_train$PAY_2)
credit_card_data_train$PAY_3 <- as.integer(credit_card_data_train$PAY_3)
credit_card_data_train$PAY_4 <- as.integer(credit_card_data_train$PAY_4)
credit_card_data_train$PAY_5 <- as.integer(credit_card_data_train$PAY_5)
credit_card_data_train$PAY_6 <- as.integer(credit_card_data_train$PAY_6)
```

## Checking structure to confirm conversion

```{r}
str(credit_card_data_train)
```

## performing lasso

```{r}
lasso_fit <- glmnet(x = as.matrix(credit_card_data_train[, -c(which(colnames(credit_card_data_train)=='default_payment_next_month'))]), y = credit_card_data_train$default_payment_next_month, alpha = 1)

#lambda = 0.5
coef(lasso_fit,s=0.5)

#lambda = 1
coef(lasso_fit,s=1)

plot(lasso_fit, xvar = "lambda", label = TRUE)
```

```{r}
library(plotmo)
```

```{r}
plot_glmnet(lasso_fit, label=8, xvar ="norm")  # label the 8 biggest final coefs
```

#use 5-fold cross validation to pick lambda

```{r}
cv_lasso_fit <- cv.glmnet(x = as.matrix(credit_card_data_train[, -c(which(colnames(credit_card_data_train)=='default_payment_next_month'))]), y = credit_card_data_train$default_payment_next_month, alpha = 1, nfolds = 5)
plot(cv_lasso_fit)
cv_lasso_fit$lambda.min
```

#-------------------------------Credit Card Default Case Study Part AB#-------------------------------


head(credit_card_data_train)
## Best Logistic Regression model chosen was with Stepwise BIC - below are the variables

```{r}
#model_stepwise_BIC.glm <- glm(default_payment_next_month ~ PAY_0 + LIMIT_BAL + PAY_5 + PAY_AMT2 + 
#                                PAY_AMT1 + BILL_AMT3 + MARRIAGE + SEX + PAY_AMT3, family=binomial, #data=credit_card_data_train)
```

### Drawing histogram of the prediction obtained using best model

```{r}
hist(predict(model_stepwise_BIC.glm))
pred_step_BIC_train <- predict(model_stepwise_BIC.glm ,type="response")
hist(pred_step_BIC_train)
```

### Drawing ROC curve

#install.packages("PRROC")

```{r}
#library(ROCR)
#library(PRROC)
```

```{r}
pred <- prediction(pred_step_BIC_train, credit_card_data_train$default_payment_next_month)
perf <- performance(pred, "tpr", "fpr")
plot(perf, colorize=TRUE, main="ROC Curve - In sample")
```

### Reporting the AUC

```{r}
unlist(slot(performance(pred, "auc"), "y.values")) # 0.7633874
```

### Drawing the 2x2 Misclassification Rate Table,  Default Cutoff Probability = 1/2 and Symmetric cost

```{r}
table(credit_card_data_train$default_payment_next_month, (pred_step_BIC_train > 0.5)*1, dnn=c("Actual values","Predicted values"))
```

#Symmetric cost

```{r}
pcut <- 1/2 
cost1 <- function(r, pi){
  mean(((r==0)&(pi>pcut)) | ((r==1)&(pi<pcut)))
}

cost1(r = credit_card_data_train$default_payment_next_month, pi = pred_step_BIC_train) # 0.179875

table(credit_card_data_train$default_payment_next_month, (pred_step_BIC_train > 0.5)*1, dnn=c("Actual values","Predicted values"))
```

### Drawing the 2x2 Misclassification Rate Table,  Default Cutoff Probability = 1/6 and Symmetric cost

```{r}
pcut <- 1/(5+1) # cost ratio 5:1
cost2 <- function(r, pi){
  weight1 <- 5
  weight0 <- 1
  c1 <- (r==1)&(pi<pcut) # logical vector - true if actual 1 but predict 0
  c0 <-(r==0)&(pi>pcut) # logical vector - true if actual 0 but predict 1
  return(mean(weight1*c1+weight0*c0))}

cost2(r = credit_card_data_train$default_payment_next_month, pi = pred_step_BIC_train) # 0.5890417

table(credit_card_data_train$default_payment_next_month, (pred_step_BIC_train > 0.167)*1, dnn=c("Actual values","Predicted values"))
```

#------------ Out of Sample Testing ------------#

### Testing on remaining 20% of the data

```{r}
pred_step_BIC_test<- predict(model_stepwise_BIC.glm, credit_card_data_test, type="response")
```

### Out-of-sample ROC curve

```{r}
pred_test <- prediction(pred_step_BIC_test, credit_card_data_test$default_payment_next_month)
perf_test <- performance(pred, "tpr", "fpr")
plot(perf_test, colorize=TRUE, main="ROC Curve - Out of sample")
```

### Reporting the AUC

```{r}
unlist(slot(performance(pred_test, "auc"), "y.values")) # 0.7574783
```

### Drawing the 2x2 Misclassification Rate Table

```{r}
pcut <- 1/2 
cost3 <- function(r, pi){
  mean(((r==0)&(pi>pcut)) | ((r==1)&(pi<pcut)))
}

cost3(r = credit_card_data_test$default_payment_next_month, pi = pred_step_BIC_test) # 0.1751667

table(credit_card_data_test$default_payment_next_month, (pred_step_BIC_test > 0.5)*1, dnn=c("Actual values","Predicted values"))
```

### Drawing the 2x2 Misclassification Rate Table,  Default Cutoff Probability = 1/6 and Symmetric cost

```{r}
pcut <- 1/(5+1) # cost ratio 5:1
cost4 <- function(r, pi){
  weight1 <- 5
  weight0 <- 1
  c1 <- (r==1)&(pi<pcut) # logical vector - true if actual 1 but predict 0
  c0 <-(r==0)&(pi>pcut) # logical vector - true if actual 0 but predict 1
  return(mean(weight1*c1+weight0*c0))}

cost4(r = credit_card_data_test$default_payment_next_month, pi = pred_step_BIC_test) # 0.565

table(credit_card_data_test$default_payment_next_month, (pred_step_BIC_test > 0.167)*1, dnn=c("Actual values","Predicted values"))
```

### Performing 5-Fold Cross Validation

```{r}
library(MASS)
library(boot)
```

### Importing the dataset with a new name

```{r}
credit_card_data_cv <- read.csv("D:/UC/Classes/Spring/Data Mining 1/Credit Card Data/default_of_credit_card_clients.csv")

credit_card_data_cv <- rename(credit_card_data_cv, default_payment_next_month = default.payment.next.month)

credit_card_data_cv = subset(credit_card_data_cv, select = -c(ID))
```

```{r}
#install.packages("caret")
```
```{r}
#install.packages("ROCR")
```
```{r}
#install.packages("pROC")
```

```{r}
library(caret)
library(ROCR)
library(pROC)
```

### ----------------- AUC on full model without cross validation

```{r}
model_full_wcv <- glm(default_payment_next_month ~ ., family=binomial, data=credit_card_data_cv)
```

### print cv scores

```{r}
log_predict_full_wcv <- predict(model_full_wcv, newdata = credit_card_data_cv, type = "response")
log_predict_full_wcv <- ifelse(log_predict_full_wcv > 0.5,1,0)
auc(credit_card_data_cv$default_payment_next_month,log_predict_full_wcv) # 0.6067
```

```{r}
pcut <- 1/(5+1) # cost ratio 5:1
cost_full_wcv <- function(r, pi){
  weight1 <- 5
  weight0 <- 1
  c1 <- (r==1)&(pi<pcut) # logical vector - true if actual 1 but predict 0
  c0 <-(r==0)&(pi>pcut) # logical vector - true if actual 0 but predict 1
  return(mean(weight1*c1+weight0*c0))}

cost_full_wcv(r = credit_card_data_cv$default_payment_next_month, pi = log_predict_full_wcv) # 0.8611667
```

### Calculating symmetric score - symmetric

```{r}
pcut <- 1/2 
cost_full_s <- function(r, pi){
  mean(((r==0)&(pi>pcut)) | ((r==1)&(pi<pcut)))
}

cost_full_s(r = credit_card_data_cv$default_payment_next_month, pi = log_predict_full_wcv) # 0.189
```

### ----------------- AUC on full model with cross validation

### define training control

```{r}
train_control <- trainControl(method = "cv", number = 5)
```

### train the model on training set

```{r}
model_full <- train(default_payment_next_month ~ .,
               data = credit_card_data_cv,
               trControl = train_control,
               method = "glm",
               family=binomial(link="logit"), na.action=na.omit)
```

### print cv scores

```{r}
log_predict_full <- predict(model_full, newdata = credit_card_data_cv)
log_predict_full <- ifelse(log_predict_full > 0.5,1,0)
auc(credit_card_data_cv$default_payment_next_month,log_predict_full) # 0.6063
```

### Calculating symmetric score - asymmetric

```{r}
pcut <- 1/(5+1) # cost ratio 5:1
cost_full <- function(r, pi){
  weight1 <- 5
  weight0 <- 1
  c1 <- (r==1)&(pi<pcut) # logical vector - true if actual 1 but predict 0
  c0 <-(r==0)&(pi>pcut) # logical vector - true if actual 0 but predict 1
  return(mean(weight1*c1+weight0*c0))}

cost_full(r = credit_card_data_cv$default_payment_next_month, pi = log_predict_full) # 0.862
```

### Calculating symmetric score - symmetric

```{r}
pcut <- 1/2 
cost_full_s <- function(r, pi){
  mean(((r==0)&(pi>pcut)) | ((r==1)&(pi<pcut)))
}

cost_full_s(r = credit_card_data_cv$default_payment_next_month, pi = log_predict_full) # 0.189
```


## Training the model using Stepwise BIC 

```{r}
#model_stepwise_BIC.glm <- glm(default_payment_next_month ~ PAY_0 + LIMIT_BAL + PAY_5 + PAY_AMT2 + 
#                                PAY_AMT1 + BILL_AMT3 + MARRIAGE + SEX + PAY_AMT3, family=binomial, #data=credit_card_data_train)

model_stepwise_BIC.glm_summary<-summary(model_stepwise_BIC.glm)

model_stepwise_BIC.glm_summary

```


#------------ 1. Using 80% Training Data

```{r}

#install.packages("rpart")

```

```{r}

library(rpart)

```


## Fit a classification tree (CART) on your 80% training data using >rpart with default arguments. Please use 5:1 
## cost ratio throughout. That is, you will specify "loss=matrix(c(0,5,10))" as in lab 6B notes. You may use the default 
## cp argument without further pruning.

```{r}

credit_rpart <- rpart(formula = default_payment_next_month ~ . , data = credit_card_data_train, method = "class", 
                      parms = list(loss=matrix(c(0,5,1,0), nrow = 2)))


credit_train_prob = predict(credit_rpart, credit_card_data_train, type="prob")

```

### Calculating values for summary table

```{r}

cost <- function(r, phat){
  weight1 <- 5
  weight0 <- 1
  pcut <- weight0/(weight1+weight0)
  c1 <- (r==1)&(phat<pcut) #logical vector - true if actual 1 but predict 0
  c0 <-(r==0)&(phat>pcut) #logical vector - true if actual 0 but predict 1
  return(mean(weight1*c1+weight0*c0))
}

cost(credit_card_data_train$default_payment_next_month, credit_train_prob) # 0.681

```



#------------ 2. Plotting Classification tree

## Plot your classification tree. Please give proper title and nice presentation of the tree figure output.

```{r}

prp(credit_rpart, extra = 1) + ggplot((title('Classification Tree')))

```


#------------ 3. Interpreting main predictor variables

## Please interpret some of the main predictor variables used to split the tree. Pick one terminal node and 
## interpret briefly of the outputs and number of observations in that particular node.


#------------ 4. ROC Curve


```{r}

#install.packages("ROCR")

```

```{r}

#library(ROCR)

```


## Draw ROC curve

```{r}

cost <- function(r, phat){
  weight1 <- 5
  weight0 <- 1
  pcut <- weight0/(weight1+weight0) 
  c1 <- (r==1)&(phat<pcut) #logical vector - true if actual 1 but predict 0
  c0 <-(r==0)&(phat>pcut) #logical vector - true if actual 0 but predict 1
  return(mean(weight1*c1+weight0*c0))
}
 
cost(credit_card_data_train$default_payment_next_month, predict(credit_rpart, credit_card_data_train, type="prob")) # 0.6815

credit_train_pred_tree <- predict(credit_rpart, credit_card_data_train, type="prob")

pred = prediction(credit_train_pred_tree[,2], credit_card_data_train$default_payment_next_month)

perf = performance(pred, "tpr", "fpr")

plot(perf, colorize=TRUE) + ggplot((title('ROC - In-sample')))

```


#------------ 5. AUC

## Report the AUC. Is it ">0.7" with satisfactory discrimatory power?

```{r}

slot(performance(pred, "auc"), "y.values")[[1]] # 0.7295294

```


### END

